Automated Topic Naming

### 2012-01-17 ese/ese.tex
unsure
- [X] In intro provide more details    - [X] In Previous work and intro add more about the comparison          between the two papers          I would actually think that it is appropriate that you mention your          previous (MSR) paper somewhere in the introduction and briefly explain          in 1 sentence how this paper extends the previous work.

%We first introduces labelled topic extraction, and then uses that technique to analyze development activity in two large-scale examples.
We begin by discussing related work in Section \ref{sec:related}.
Next, we describe how we generated our data (Section \ref{sec:wordlist}). For semi-unsupervised classification (Section \ref{sec:unsuplabelling}), we
begin by creating word-lists to signify when a topic matches an NFR label. We then apply our classifier and analyze the results. 
%and how we created the word-lists used in unsupervised classification. 
%We show that labels with their topics can be learned and used to classify other data-sets, either without training 
%Our goal is to label a given topic with either an NFR from our taxonomy,
 %Section \ref{sec:unsuplabelling} presents our technique for using word-lists to do unsupervised classification, and describes the results.
In Section \ref{sec:suplabelling}, we manually annotate the topics, and use those annotations as training data for supervised classification.  
%We then present visualizations of named topics and their trends over time to aid communication and analysis. 
To demonstrate an application of labelled topic extraction, we use an exploratory case study of three open source database systems to show how named
topics can be compared between projects  (Section \ref{sec:analysis}). 
The paper concludes with a discussion of limitations (Section \ref{sec:limit}), and future work.

@@

>>>>

%We first introduces labelled topic extraction, and then uses that technique to analyze development activity in two large-scale examples.
We begin by discussing related work in Section \ref{sec:related}.
Next, we describe how we generated our data (Section \ref{sec:wordlist}). For semi-unsupervised classification (Section \ref{sec:unsuplabelling}), we
begin by creating word-lists to signify when a topic matches an NFR label. We then apply our classifier and analyze the results. 
%and how we created the word-lists used in unsupervised classification. 
%We show that labels with their topics can be learned and used to classify other data-sets, either without training 
%Our goal is to label a given topic with either an NFR from our taxonomy,
 %Section \ref{sec:unsuplabelling} presents our technique for using word-lists to do unsupervised classification, and describes the results.

This work extends our previous work~\cite{msr2011}, published at The
Working Conference on Mining Software Repositories 2011
(MSR'2011). 
Within this new paper that builds up upon the previous
work, we added more machine learning results and another case-study: PostgreSQL. 
We used two authors to
each annotate the same PostgreSQL topics in order to compare
them. 
Thus we used this new case-study to test inter-rater
reliability, described in Section \ref{sec:inter-rater}. 
In Section
\ref{sec:developers}, we further extended the MSR'2011 paper with an
analysis of PostgreSQL authors and their association with NFRs and
topics.

In Section \ref{sec:suplabelling}, we manually annotate the topics, and use those annotations as training data for supervised classification.  
%We then present visualizations of named topics and their trends over time to aid communication and analysis. 
To demonstrate an application of labelled topic extraction, we use an exploratory case study of three open source database systems to show how named
topics can be compared between projects  (Section \ref{sec:analysis}). 
The paper concludes with a discussion of limitations (Section \ref{sec:limit}), and future work.

@@

\label{sec:developers}
